clean_census_data_from_GSS

### 2020-12-18 input/post-stratification data/clean_census_data.Rmd
post stratification

```{r}
#Create cell counts:
cell_counts <- census %>% group_by(province, sex, as.factor(age), employed, bornin_canada, edu) %>% count() %>% rename(age = "as.factor(age)")
#Create a .csv file
write.csv(cell_counts, "census_cleaned.csv")
```

>>>>

```{r}
#Create cell counts:
cell_counts <- census %>% group_by(province, sex, as.factor(age), employed, bornin_canada, edu) %>% count()
#Create a .csv file
write.csv(cell_counts, "census_cleaned.csv")
```
